---
title: "R Notebook"
output: html_notebook
---

# Analyzing dataset of WES(whole exome sequencing) result of 10 pancreatic cancer patients(advanced)

1. Find out commonly mutated genes in 10 patients
2. Find out specifically mutated genes in each patient
3. Calculate the percentage of commonly mutated genes in TCGA-GDC dataset
4. To check if the specifically mutated genes are reported in the PUBMED site

```{r}
library(tidyverse)
library(readxl)
```


```{r}
d<-read_excel("~/Downloads/Pancreatic Cancer All Cell Lines_HIGH,MODERATE_DUP REMOVED.xlsx")
d<-as_tibble(d)
```
```{r}
genes<-d[ ,c(1:5,11,12,18,19,30,31,72:81) ]
```

```{r}
# Select Polyphe2 colomn which only contains "D"
x<-c("B", "P")
x<-grep(paste(x, collapse="|"),genes$`Polyphen2 HVAR Pred`)
genes<-genes[-x, ]
genes<-genes[grep("D",genes$`Polyphen2 HVAR Pred`), ]
```


```{r}
#Select SIFT pred column which only contains "D"
genes<-genes[-grep("T",genes$`SIFT Pred`), ]
```

```{r}
cal<-function(dat,a){
  x<-which(dat[ ,a]!=0)
x<-dat[x,1:10]
return(x)
}
```

```{r}
a<-cal(genes, 10)
b<-cal(genes, 11)
c<-cal(genes, 12)
d<-cal(genes, 13)
e<-cal(genes, 14)
f<-cal(genes, 15)
g<-cal(genes, 16)
h<-cal(genes, 17)
i<-cal(genes, 18)
j<-cal(genes, 19)
```


```{r}
# Commonly mutated genes in all 10 patients
common_genes<-Reduce(intersect,list(unique(a$Gene_Name),unique(b$Gene_Name),unique(c$Gene_Name),unique(d$Gene_Name),unique(e$Gene_Name),unique(f$Gene_Name),unique(g$Gene_Name),unique(h$Gene_Name),unique(i$Gene_Name),unique(j$Gene_Name)))
common_genes<-as_tibble(common_genes)
common_genes
```

```{r}
#Commonly mutated positons in all 10 patients
common_pos<-Reduce(intersect,list(a$POS, b$POS, c$POS, d$POS, e$POS, f$POS, g$POS, h$POS, i$POS, j$POS))
common_pos<-as_tibble(common_pos)
common_pos
```

```{r}
specific<- list(A = unique(a$Gene_Name),
            B = unique(b$Gene_Name),
            C = unique(c$Gene_Name),
            D = unique(d$Gene_Name),
            E = unique(e$Gene_Name),
            f = unique(f$Gene_Name),
            G = unique(g$Gene_Name),
            H = unique(h$Gene_Name),
            I = unique(i$Gene_Name),
            J = unique(j$Gene_Name))
specific_gene<-lapply(1:length(specific), function(n) setdiff(specific[[n]], unlist(specific[-n])))
```


```{r}
# specifically mutated genes which are found in each patient
specific_a<-as_tibble(specific_gene[[1]])
specific_b<-as_tibble(specific_gene[[2]])
specific_c<-as_tibble(specific_gene[[3]])
specific_d<-as_tibble(specific_gene[[4]])
specific_e<-as_tibble(specific_gene[[5]])
specific_f<-as_tibble(specific_gene[[6]])
specific_g<-as_tibble(specific_gene[[7]])
specific_h<-as_tibble(specific_gene[[8]])
specific_i<-as_tibble(specific_gene[[9]])
specific_j<-as_tibble(specific_gene[[10]])
```


```{r}
library(maftools)
tcga<-read.maf(maf="~/Downloads/TCGA.PAAD.somaticsniper.0ca0083b-4c11-47f2-b672-d74911f50b89.DR-10.0.somatic.maf")
```

```{r}
tcga_genes<-getGeneSummary(tcga)
```


```{r}
common_gene<-Reduce(intersect,list(unique(a$Gene_Name),unique(b$Gene_Name),unique(c$Gene_Name),unique(d$Gene_Name),unique(e$Gene_Name),unique(f$Gene_Name),unique(g$Gene_Name),unique(h$Gene_Name),unique(i$Gene_Name),unique(j$Gene_Name)))
common_gene
```

```{r}
# percentage of commonly mutated genes in TCGA-GDC dataset
mean(tcga_genes$Hugo_Symbol%in%common_gene)
```
[ACTBL2](https://www.ncbi.nlm.nih.gov/pubmed/27989943)
No result for the correlation of TBL3(transducin beta like 3) with cancer


