---
title: "R Notebook"
output: html_notebook
---


# Chapter 9 Visualizing data distributions
## 9.1 Variable types
We will be working with two types of variables: categorical and numeric. When each entry in a vector comes from one of a small number of groups, we refer to the data as _categorical_ data. 
## 9.2 Case study: describing student heights
Pretend that we have to describe the heights of our classmates to ET, an extraterrestrial that has never seen humans. As a first step, we need to collect data. To do this, we ask students to report their heights in inches. We ask them to provide sex information because we know there are two different distributions by sex. We collect the data and save it in a data frame:

```{r}
library(tidyverse)
library(dslabs)
data(heights)
head(heights)
```
One way to convey the heights to ET is to simply send him this list of 1050 heights. But there are much more effective ways to convey this information, and understanding the concept of a distribution will help. To simplify the explanation, we first focus on male heights. We examine the female height data in Section 9.14 .

## 9.3 Distribution function
It turns out that, in some cases, the average and the standard deviation are pretty much all we need to understand the data. We will learn data visualization techniques that will help us determine when this two number summary is appropriate. These same techniques will serve as an alternative for when two numbers are not enough.

The most basic statistical summary of a list of objects or numbers is its distribution. The simplest way to think of a distribution is as a compact description of a list with many entries. This concept should not be new for readers of this book. For example, with categorical data, the distribution simply describes the proportion of each unique category. The sex represented in the heights dataset is:
```{r}
library(frequency)
heights$sex%>%
  freq()
```

## 9.4 Cumulative distribution functions
Statistics textbooks teach us that a more useful way to define a distribution for numeric data is to define a function that reports the proportion of the data below  a for all possible values of  a . This function is called the cumulative distribution function (CDF). In statistics, the following notation is used: F(a)=Pr(x≤a)
Here is a plot of  F  for the male height data:

Similar to what the frequency table does for categorical data, the CDF defines the distribution for numerical data.
A final note: because CDFs can be defined mathematically the word empirical is added to make the distinction when data is used. We therefore use the term empirical CDF (eCDF).

## 9.5 Histograms
Histograms are much preferred because they greatly facilitate answering such questions. Histograms sacrifice just a bit of information to produce plots that are much easier to interpret.A histogram is similar to a barplot, but it differs in that the x-axis is numerical, not categorical.

## 9.6 Smoothed density
Smooth density plots are aesthetically more appealing than histograms.
In this plot, we no longer have sharp edges at the interval boundaries and many of the local peaks have been removed. Also, the scale of the y-axis changed from counts to density.

### 9.6.1 Interpreting the y-axis
Note that interpreting the y-axis of a smooth density plot is not straightforward. It is scaled so that the area under the density curve adds up to 1. If you imagine we form a bin with a base 1 unit in length, the y-axis value tells us the proportion of values in that bin. However, this is only true for bins of size 1. For other size intervals, the best way to determine the proportion of data in that interval is by computing the proportion of the total area contained in that interval. 
### 9.6.2 Densities permit stratification
As a final note, we point out that an advantage of smooth densities over histograms for visualization purposes is that densities makes it easier to compare two distributions.

## 9.7 Exercises
1. In the ```murders``` dataset, the region is a categorical variable and the following is its distribution:
To the closet 5%, what proportion of the states are in the North Central region?
**0.25**

2. Which of the following is true:

A. The graph above is a histogram.

**B. The graph above shows only four numbers with a bar plot.**

C. Categories are not numbers, so it does not make sense to graph the distribution.

D. The colors, not the height of the bars, describe the distribution.

3. The plot below shows the eCDF for male heights:
Based on the plot, what percentage of males are shorter than 75 inches?

A. 100%

**B. 95%**

C. 80%

D. 72 inches

4. To the closest inch, what height m has the property that 1/2 of the male students are taller than m and 1/2 are shorter?

A. 61 inches

B. 64 inches

**C. 69 inches**

D. 74 inches

5. Here is an eCDF of the murder rates across states:

Knowing that there are 51 states (counting DC) and based on this plot, how many states have murder rates larger than 10 per 100,000 people?

**A. 1**

B. 5

C. 10

D. 50

6. Based on the eCDF above, which of the following statements are true:

A. About half the states have murder rates above 7 per 100,000 and the other half below.

B. Most states have murder rates below 2 per 100,000.

C. All the states have murder rates above 2 per 100,000.

**D. With the exception of 4 states, the murder rates are below 5 per 100,000.**

7. Below is a histogram of male heights in our heights dataset:

Based on this plot, how many males are between 63.5 and 65.5?

A. 10

B. 24

C. 34

D. 100
**about 46**

8. About what percentage are shorter than 60 inches?

**A. 1%**

B. 10%

C. 25%

D. 50%

9. Based on the density plot below, about what proportion of US states have populations larger than 10 million?

A. 0.02

**B. 0.15**

C. 0.50

D. 0.55

10. Below are three density plots. Is it possible that they are from the same dataset?
Which of the following statements is true:

A. It is impossible that they are from the same dataset.

B. They are from the same dataset, but the plots are different due to code errors.

C. They are the same dataset, but the first and second plot undersmooth and the third oversmooths.

**D. They are the same dataset, but the first is not in the log scale, the second undersmooths and the third oversmooths.**

## 9.8 The normal distribution
The normal distribution, also known as the bell curve and as the Gaussian distribution, is one of the most famous mathematical concepts in history. A reason for this is that approximately normal distributions occur in many situations, including gambling winnings, heights, weights, blood pressure, standardized test scores, and experimental measurement errors.
Rather than using data, the normal distribution is defined with a mathematical formula. For any interval  (a,b) , the proportion of values in that interval can be computed using this formula: note that it is completely defined by just two parameters:  m  and  s . The rest of the symbols in the formula represent the interval ends that we determine,  a  and  b , and known mathematical constants π  and  e . These two parameters,  m  and  s , are referred to as the _average_ (also called the _mean_) and the _standard deviation_ (SD) of the distribution respectively.
The distribution is symmetric, centered at the average, and most values (about 95%) are within 2 SDs from the average. 

For a list of numbers contained in a vector x, the average is defined as:
```{r}
# m <- sum(x) / length(x)
```

and the SD is defined as:
```{r}
# s <- sqrt(sum((x-mu)^2) / length(x))
```

which can be interpreted as the **average distance between values and their average**.
Let’s compute the values for the height for males which we will store in the object  x :
```{r}
index <- heights$sex=="Male"
x <- heights$height[index]
```
The pre-built functions ```mean``` and ```sd``` (note that for reasons explained in Section 17.2, ```sd``` divides by ```length(x)-1``` rather than ```length(x)```) can be used here:
```{r}
m <- mean(x)
s <- sd(x)
c(average = m, sd = s)
```
Here is a plot of the smooth density and the normal distribution with mean = 69.3 and SD = 3.6 plotted as a black line with our student height smooth density in blue:

The normal distribution does appear to be quite a good approximation here. We now will see how well this approximation works at predicting the proportion of values within intervals.

## 9.9 Standard units
For data that is approximately normally distributed, it is convenient to think in terms of standard units. The standard unit of a value tells us how many standard deviations away from the average it is. Specifically, for a value ```x``` from a vector ```X```, we define the value of ```x``` in standard units as ```z = (x - m)/s``` with ```m``` and ```s``` the average and standard deviation of ```X``` respectively.
Because the maximum of  e^(−(z^2)/2)  is when  z=0 , this explains why the maximum of the distribution occurs at the average. It also explains the symmetry since  −z^2/2  is symmetric around 0.  Second, note that if we convert the normally distributed data to standard units, we can quickly know if, for example, a person is about average ( z=0 ), one of the largest ( z≈2 ), one of the smallest ( z≈−2 ) or an extremely rare occurrence ( z>3  or  z<−3 ). Remember that it does not matter what the original units are, these rules apply to any data that is approximately normal.

In R, we can obtain standard units using the function scale:
```{r}
z <- scale(x)
```

Now to see how many men are within 2 SDs from the average, we simply type:
```{r}
mean(abs(z) < 2)
```
The proportion is about 95%, which is what the normal distribution predicts! To further confirm that, in fact, the approximation is a good one, we can use quantile-quantile plots.

## 9.10 Quantile-quantile plots
A systematic way to assess how well the normal distribution fits the data is to check if the observed and predicted proportions match. In general, this is the approach of the quantile-quantile plot (QQ-plot). First let’s define the theoretical quantiles for the normal distribution. In statistics books we use the symbol  Φ(x)  to define the function that gives us the probability of a standard normal distribution being smaller than  x . In R, we can evaluate  Φ  using the ```pnorm``` function:
```{r}
pnorm(-1.96)
```
The inverse function  Φ^(−1)(x)  gives us the theoretical quantiles for the normal distribution. So, for example,  Φ^(−1)(0.975)=1.96 . In R, we can evaluate the inverse of  Φ  using the ```qnorm``` function.
```{r}
qnorm(0.975)
```
Note that these calculations are for the standard normal distribution by default (mean = 0, standard deviation = 1), but we can also define these for any normal distribution. We can do this using the ```mean``` and ```sd``` arguments in the ```pnorm``` and ```qnorm``` function. For example, we can use ```qnorm``` to determine quantiles of a distribution with a specific average and standard deviation
```{r}
qnorm(0.975, mean = 5, sd = 2)
```
For the normal distribution, all the calculations related to quantiles are done without data, thus the name _theoretical quantiles_. But quantiles can be defined for any distribution, including an empirical one. So if we have data in a vector  x , we can define the quantile associated with any proportion  p  as the  q  for which the proportion of values below  q  is  p . Using R code, we can define ```q``` as the value for which ```mean(x <= q) = p```. Notice that not all  p  have a  q  for which the proportion is exactly  p . There are several ways of defining the best  q  as discussed in the help for the ```quantile``` function.

To give a quick example, for the male heights data, we have that:
```{r}
mean(x <= 69.5)
```
So about 50% are shorter or equal to 69 inches. This implies that if  p=0.50  then  q=69.5 .

The idea of a QQ-plot is that if your data is well approximated by normal distribution then the quantiles of your data should be similar to the quantiles of a normal distribution. To construct a QQ-plot, we do the following:
1. Define a vector of  m  proportions  p1,p2,…,pm .
2. Define a vector of quantiles  q1,…,qm  for your data for the proportions  p1,…,pm . We refer to these as the sample quantiles.
3. Define a vector of theoretical quantiles for the proportions  p1,…,pm  for a normal distribution with the same average and standard deviation as the data.
4. Plot the sample quantiles versus the theoretical quantiles.
Let’s construct a QQ-plot using R code. Start by defining the vector of proportions.
```{r}
p <- seq(0.05, 0.95, 0.05)
```

To obtain the quantiles from the data, we can use the ```quantile``` function like this:
```{r}
sample_quantiles <- quantile(x, p)
sample_quantiles
```
To obtain the theoretical normal distribution quantiles with the corresponding average and SD, we use the ```qnorm``` function:
```{r}
theoretical_quantiles <- qnorm(p, mean = mean(x), sd = sd(x))
theoretical_quantiles
```
To see if they match or not, we plot them against each other and draw the identity line:
```{r}
qplot(theoretical_quantiles, sample_quantiles) + geom_abline()
```

Notice that this code becomes much cleaner if we use standard units:
```{r}
sample_quantiles <- quantile(z, p)
theoretical_quantiles <- qnorm(p) 
qplot(theoretical_quantiles, sample_quantiles) + geom_abline()
```

The above code is included to help describe QQ-plots. However, in practice it is easier to use the **ggplot2** code described in Section 9.16:
```{r}
heights %>% filter(sex=="Male") %>%
  ggplot(aes(sample = scale(height))) + 
  geom_qq() +
  geom_abline()
```
While for the illustration above we used 20 quantiles, the default from the ```geom_qq``` function is to use as many quantiles as data points.

## 9.11 Percentiles
For the normal distribution the _median_ and average are the same, but this is generally not the case.

Another special case that receives a name are the _quartiles_, which are obtained when setting  p=0.25,0.50 , and  0.75 .

## 9.12 Boxplots
A five-number summary composed of the range along with the quartiles (the 25th, 50th, and 75th percentiles). We plot these numbers as a “box” with “whiskers” like this: with the box defined by the 25% and 75% percentile and the whiskers showing the range. The distance between these two is called the _interquartile_ range. The two points are outliers according to Tukey’s definition. The median is shown with a horizontal line. Today, we call these _boxplots_.

## 9.13 Stratification
In data analysis we often divide observations into groups based on the values of one or more variables associated with those observations. For example in the next section we divide the height values into groups based on a sex variable: females and males. We call this procedure _stratification_ and refer to the resulting groups as _strata_.

## 9.14 Case study: describing student heights (continued)
 In this case, we report back to ET a very succinct summary: male heights follow a normal distribution with an average of 69.3 inches and a SD of 3.6 inches. However, to provide a complete picture we need to also provide a summary of the female heights.We learned that boxplots are useful when we want to quickly compare two or more distributions. The plot immediately reveals that males are, on average, taller than females. The standard deviations appear to be similar. But does the normal approximation also work for the female height data collected by the survey. We expect that they will follow a normal distribution, just like males. However, exploratory plots reveal that the approximation is not as useful:
 
 We see something we did not see for the males: the density plot has a second “bump”. Also, the QQ-plot shows that the highest points tend to be taller than expected by the normal distribution. Finally, we also see five points in the QQ-plot that suggest shorter than expected heights for a normal distribution. When reporting back to ET, we might need to provide a histogram rather than just the average and standard deviation for the female heights.

However, go back and read Tukey’s quote. We have noticed what we didn’t expect to see. If we look at other female height distributions, we do find that they are well approximated with a normal distribution. So why are our female students different? Is our class a requirement for the female basketball team? Are small proportions of females claiming to be taller than they are? Another, perhaps more likely, explanation is that in the form students used to enter their heights, ```FEMALE``` was the default sex and some males entered their heights, but forgot to change the sex variable. In any case, data visualization has helped discover a potential flaw in our data.
```{r}
heights %>% filter(sex=="Female") %>% top_n(5, desc(height)) %>% pull(height)
```
Because these are reported heights, a possibility is that the student meant to enter 5’1“, 5’2”, 5’3" or 5’5“.

## 9.15 Exercises

1. Define variables containing the heights of males and females like this:
```{r}
library(dslabs)
data(heights)
male <- heights$height[heights$sex=="Male"]
female <- heights$height[heights$sex=="Female"]
```

How many measurements do we have for each?
**812, 238**
```{r}
str(male)
str(female)
```
2. Suppose we can’t make a plot and want to compare the distributions side by side. We can’t just list all the numbers. Instead, we will look at the percentiles. Create a five row table showing ```female_percentiles``` and ```male_percentiles``` with the 10th, 30th, 50th, …, 90th percentiles for each sex. Then create a data frame with these two as columns.
```{r}
p<-seq(0.1,0.9,0.2)
female_percentiles<- quantile(female, p)
male_percentiles<-quantile(male,p)
data_frame(p, female_percentiles, male_percentiles)
```
3. Study the following boxplots showing population sizes by country:
Which continent has the country with the biggest population size?
**Asia**

4. What continent has the largest median population size?
**Africa**

5. What is median population size for Africa to the nearest million?
**10**

6. What proportion of countries in Europe have populations below 14 million?

A. 0.99

**B. 0.75**

C. 0.50

D. 0.25

7. If we use a log transformation, which continent shown above has the largest interquartile range?
**Americas**

8. Load the height data set and create a vector ```x``` with just the male heights:
```{r}
library(dslabs)
data(heights)
x <- heights$height[heights$sex=="Male"]
```

What proportion of the data is between 69 and 72 inches (taller than 69, but shorter or equal to 72)? Hint: use a logical operator and ```mean```.
```{r}
mean(x>69&x<=72)
```

9. Suppose all you know about the data is the average and the standard deviation. Use the normal approximation to estimate the proportion you just calculated. Hint: start by computing the average and standard deviation. Then use the ```pnorm``` function to predict the proportions.
```{r}
pnorm(72, mean=mean(x), sd=sd(x))-pnorm(69, mean=mean(x), sd=sd(x))
```
10. Notice that the approximation calculated in question two is very close to the exact calculation in the first question. Now perform the same task for more extreme values. Compare the exact calculation and the normal approximation for the interval (79,81]. How many times bigger is the actual proportion than the approximation?
```{r}
mean(x>79&x<=81)/(pnorm(81, mean=mean(x), sd=sd(x))-pnorm(79, mean=mean(x), sd=sd(x)))
```
11. Approximate the distribution of adult men in the world as normally distributed with an average of 69 inches and a standard deviation of 3 inches. Using this approximation, estimate the proportion of adult men that are 7 feet tall or taller, referred to as seven footers. Hint: use the ```pnorm``` function.
```{r}
1-pnorm(7*12,mean=69, sd=3)
```

12. There are about 1 billion men between the ages of 18 and 40 in the world. Use your answer to the previous question to estimate how many of these men (18-40 year olds) are seven feet tall or taller in the world?
```{r}
(1-pnorm(7*12, mean=69,sd=3))*10^9
```
13. There are about 10 National Basketball Association (NBA) players that are 7 feet tall or higher. Using the answer to the previous two questions, what proportion of the world’s 18 to 40 year old _seven footers_ are in the NBA?
```{r}
10/287
```

14. Repeat the calculations performed in the previous question for Lebron James’ height: 6 feet 8 inches. There are about 150 players that are at least that tall.
```{r}
6*12+8
a<-(1-pnorm(80, mean=69, sd=3))*10^9
150/a
```

15. In answering the previous questions, we found that it is not at all rare for a seven footer to become an NBA player. What would be a fair critique of our calculations:

A. Practice and talent are what make a great basketball player, not height.

B. The normal approximation is not appropriate for heights.

**C. As seen in question 3, the normal approximation tends to underestimate the extreme values. It’s possible that there are more seven footers than we predicted.**

D. As seen in question 3, the normal approximation tends to overestimate the extreme values. It’s possible that there are less seven footers than we predicted.

## 9.16 ggplot2 geometries
In Chapter 8, we introduced the **ggplot2** package for data visualization. Here we demonstrate how to generate plots related to distributions, specifically the plots shown earlier in this chapter.

### 9.16.1 Barplots
To generate a barplot we can use the ```geom_bar``` geometry. The default is to count the number of each category and draw a bar. Here is the plot for the regions of the US.
```{r}
murders %>% ggplot(aes(region))+ geom_bar()
```

We often already have a table with a distribution that we want to present as barplot. Here is an example such a table:
```{r}
data(murders)
tab <- murders %>% 
  count(region) %>% 
  mutate(proportion = n/sum(n))
tab
```

We no longer want ```geom_bar``` to count, but rather just plot a bar to the height provided by the ```proportion``` variable. For this we need to provide ```x``` (the categories) and ```y``` (the values) and use the ```stat="identity"``` option.
```{r}
tab %>% ggplot(aes(region, proportion)) + geom_bar(stat = "identity")
```
### 9.16.2 Histograms
To generate histograms we use ```geom_histogram```. By looking at the help file for this function, we learn that the only required argument is ```x```, the variable for which we will construct a histogram. We dropped the ```x``` because we know it is the first argument. The code looks like this:
```{r}
heights %>% 
  filter(sex == "Female") %>% 
  ggplot(aes(height)) + 
  geom_histogram()
```

If we run the code above, it gives us a message:
>```stat_bin()``` using ```bins = 30```. Pick better value with ```binwidth```.

We previously used a bin size of 1 inch, so the code looks like this:
```{r}
heights %>% 
  filter(sex == "Female") %>% 
  ggplot(aes(height)) + 
  geom_histogram(binwidth = 1)
```

Finally, if for aesthetic reasons we want to add color, we use the arguments described in the help file. We also add labels and a title:
```{r}
heights %>% 
  filter(sex == "Female") %>% 
  ggplot(aes(height)) +
  geom_histogram(binwidth = 1, fill = "blue", col = "black") +
  xlab("Male heights in inches") + 
  ggtitle("Histogram")
```
### 9.16.3 Density plots
To create a smooth density, we use the ```geom_density```. Here the is data previously shown as a histogram:
```{r}
heights %>% 
  filter(sex == "Female") %>%
  ggplot(aes(height)) +
  geom_density()
```

To fill in with color, we can use the ```fill``` argument.
```{r}
heights %>% 
  filter(sex == "Female") %>%
  ggplot(aes(height)) +
  geom_density(fill="blue", col="grey")
```

To change the smoothness of the density, we use the ```adjust``` argument to multiply the default value by that ```adjust```. For example, if we want the bandwidth to be twice as big we use:
```{r}
heights %>%
  filter(sex == "Female") %>%
  ggplot(aes(height)) +
  geom_density(fill="blue", adjust=2)
```
### 9.16.4 Boxplots
The geometry for boxplot is ```geom_boxplot```. As discussed, boxplots are useful for comparing distributions. For example, below are the previously shown heights for women, but compared to men. For this geometry, we need arguments ```x``` as the categories, and ```y``` as the values.
```{r}
heights%>%
  ggplot(aes(x=sex,y=height))+
  geom_boxplot()
```

### 9.16.5 QQ-plots
For qq-plots we use the ```geom_qq geometry```. From the help file, we learn that we need to specify the ```sample``` (we will learn about samples in a later chapter). Here is the qqplot for men heights.
```{r}
heights %>% filter(sex=="Male") %>%
  ggplot(aes(sample = height)) +
  geom_qq()
```
By default, the sample variable is compared to a normal distribution with average 0 and standard deviation 1. To change this, we use the ```dparams``` arguments based on the help file. Adding an identity line is as simple as assigning another layer. For straight lines, we use the ```geom_abline``` function. The default line is the identity line (slope = 1, intercept = 0).
```{r}
params <- heights %>% filter(sex=="Male") %>%
  summarize(mean = mean(height), sd = sd(height))

heights %>% filter(sex=="Male") %>%
  ggplot(aes(sample = height)) +
  geom_qq(dparams = params) +
  geom_abline()
```

Another option here is to scale the data first and then make a qqplot against the standard normal.
```{r}
heights %>% 
  filter(sex=="Male") %>%
  ggplot(aes(sample = scale(height))) + 
  geom_qq() +
  geom_abline()
```
### 9.16.6 Images
Images were not needed for the concepts described in this chapter, but we will use images in Section 11.14, so we introduce the two geometries used to create images: **geom_tile** and **geom_raster**. They behave similarly; to see how they differ, please consult the help file. To create an image in **ggplot2** we need a data frame with the x and y coordinates as well as the values associated with each of these. Here is a data frame.

```{r}
x <- expand.grid(x = 1:12, y = 1:10) %>% 
  mutate(z = 1:120) 
```

Note that this is the tidy version of a matrix, ```matrix(1:120, 12, 10)```. To plot the image we use the following code:
```{r}
x %>% ggplot(aes(x, y, fill = z)) + 
  geom_raster()
```
With these images you will often want to change the color scale. This can be done through the ```scale_fill_gradientn``` layer.
```{r}
x %>% ggplot(aes(x, y, fill = z)) + 
  geom_raster() + 
  scale_fill_gradientn(colors =  terrain.colors(10))
```

### 9.16.7 Quick plots
In Section 8.13 we introduced ```qplot``` as a useful function when we need to make a quick scatterplot. We can also use ```qplot``` to make histograms, density plots, boxplot, qqplots and more. Although it does not provide the level of control as ```ggplot```, ```qplot``` is definitely useful as it permits us to make a plot with a short snippet of code.

Suppose we have the male heights in an object ```x```:
```{r}
x <- heights %>% 
  filter(sex=="Male") %>% 
  pull(height)
```

To make a quick histogram we can use:
```{r}
qplot(x)
```
The function guesses that we want to make a histogram because we only supplied one variable. In Section 8.13 we saw that if we supply ```qplot``` two variables, it automatically makes a scatterplot.

To make a quick qqplot you have to use the ```sample``` argument. Note that we can add layers just as we do with ```ggplot```.
```{r}
qplot(sample = scale(x)) + geom_abline()
```

If we supply a factor and a numeric vector, we obtain a plot like the below. Note that in the code below we are using the ```data``` argument. Because the data frame is not the first argument in ```qplot```, we have to use the dot operator.
```{r}
heights %>% qplot(sex, height, data = .)
```
We can also select a specific geometry by using the ```geom``` argument. So to convert the plot above to a boxplot, we use the following code:
```{r}
heights %>% qplot(sex, height, data = ., geom = "boxplot")
```
We can also use the ```geom``` argument to generate a density plot instead of a histogram:

```{r}
qplot(x, geom = "density")
```
Although not as much as with```ggplot```, we do have some flexibility to improve the results of ```qplot```. Looking at the help file we see several ways in which we can improve the look of the histogram above. Here is an example:
```{r}
qplot(x, bins=15, color = I("black"), xlab = "Population")
```
Technical note: The reason we use ```I("black")``` is because we want ```qplot``` to treat ```"black"``` as a character rather than convert it to a factor, which is the default behavior within ```aes```, which is internally called here. In general, the function ```I``` is used in R to say “keep it as it is”.

## 9.17 Exercises
1. Now we are going to use the ```geom_histogram``` function to make a histogram of the heights in the ```height``` data frame. When reading the documentation for this function we see that it requires just one mapping, the values to be used for the histogram. Make a histogram of all the plots.

What is the variable containing the heights?

A. ```sex```

B. ```heights```

**C. ```height```**

D. ```heights$height```

2. Now create a ggplot object using the pipe to assign the heights data to a ggplot object. Assign ```height``` to the x values through the ```aes``` function.
```{r}
heights%>%
  ggplot(aes(height))
```
3. Now we are ready to add a layer to actually make the histogram. Use the object created in the previous exercise and the ```geom_histogram``` function to make the histogram.
```{r}
heights%>%
  ggplot(aes(height))+
  geom_histogram()
```
4. Note that when we run the code in the previous exercise we get the warning: ```stat_bin()``` using ```bins = 30```. Pick better value with ```binwidth```.
Use the ```binwidth``` argument to change the histogram made in the previous exercise to use bins of size 1 inch.
```{r}
heights %>% 
  ggplot(aes(height)) + 
  geom_histogram(binwidth = 1)
```
5. Instead of a histogram, we are going to make a smooth density plot. In this case we will not make an object, but instead render the plot with one line of code. Change the geometry in the code previously used to make a smooth density instead of a histogram.
```{r}
heights %>% 
  ggplot(aes(height)) + 
  geom_density()
```
6. Now we are going to make a density plot for males and females separately. We can do this using the ```group``` argument. We assign groups via the aesthetic mapping as each point needs to a group before making the calculations needed to estimate a density.
```{r}
heights%>%
  ggplot(aes(height, group=sex))+
  geom_density()
```
7. We can also assign groups through the color argument. This has the added benefit that it uses ```color``` to distinguish the groups. Change the code above to use color
```{r}
heights%>%
  ggplot(aes(height, color=sex))+
  geom_density()
```
8. We can also assign groups through the ```fill``` argument. This has the added benefit that it uses colors to distinguish the groups, like this:
```{r}
heights %>% 
  ggplot(aes(height, fill = sex)) + 
  geom_density() 
```
However, here the second density is drawn over the other. We can make the curves more visible by using alpha blending to add transparency. Set the alpha parameter to 0.2 in the geom_density function to make this change.
```{r}
heights %>% 
  ggplot(aes(height, fill = sex)) + 
  geom_density(alpha=0.2) 
```

